\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs, longtable}
\usepackage{enumitem}
\usepackage{setspace}

% Color definitions for listings
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

% Listing style for C code
\lstdefinestyle{cstyle}{
    language=C,
    backgroundcolor=\color{backcolour},    % Light grey background
    commentstyle=\color{codegreen},        % Green for comments
    keywordstyle=\color{magenta},          % Magenta for keywords
    numberstyle=\tiny\color{codegray},     % Grey for line numbers
    stringstyle=\color{codepurple},        % Purple for strings
    basicstyle=\ttfamily\small,            % Small typewriter font
    breakatwhitespace=false,               % Allows breaking at whitespace
    breaklines=true,                       % Automatic line breaking
    postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},  % Arrow for line continuation
    captionpos=b,                          % Caption position at bottom
    keepspaces=true,                       % Keeps spaces for alignment
    numbers=left,                          % Line numbers on left
    numbersep=5pt,                         % Space between line numbers and code
    showspaces=false,                      % Do not show spaces with special characters
    showstringspaces=false,                % Do not show spaces within strings
    showtabs=false,                        % Do not show tabs within strings
    tabsize=2                              % Tab size of 2 spaces
}

\geometry{
    a4paper,
    total={170mm,257mm},
    left=20mm,
    top=20mm,
}

\title{Paper, Scissors, Rock Project}
\author{Abraham J. Reines}
\date{\today}

\begin{document}

\maketitle

\section{Project Overview}
This project has concurrent programming to simulate game "Paper, Scissors, Rock" using multiple processes in Unix. system has three components: `play` program, `referee` program, and multiple `player` programs. 

\section{Implementation Details}
\subsection{Play Program}
`play` program initiates game by creating player processes and a referee process. All processes are correctly synchronized and communicates game results.

\subsection{Referee Program}
referee program controls game flow, receives choices from players, determines winner, and sends results back to play program.

\subsection{Player Programs}
Each player program represents a participant in game. These programs send their game choices to referee and wait for results.

\section{Execution}
\subsection{Compiling Programs}
To compile programs use GNU Compiler Collection (gcc). 

\begin{lstlisting}[language=bash]
make -f makefile.mak
\end{lstlisting}

\subsection{Running Simulation}
To run simulation open terminal windows. execute programs different terminals:

\begin{enumerate}
    \item \textbf{Terminal 1: Start Play Program}
    In first terminal, 
    \begin{lstlisting}[language=bash]
    ./play
    \end{lstlisting}

    \item \textbf{Terminal 2: Start Referee Program}
    Open a second terminal and start `referee` program:
    \begin{lstlisting}[language=bash]
    ./referee
    \end{lstlisting}

    \item \textbf{Terminal 3 : Start Player Programs}
    Each player will run in a separate terminal. 
    \begin{lstlisting}[language=bash]
    ./player
    \end{lstlisting}
    Repeat this step in each new terminal for additional players.
\end{enumerate}

\textbf{Note:}  `play` program is executed before `referee` and `player` programs.

\section{Project Execution and Compliance Report}

\subsection{Execution on 'stu'}
This project was tested to compile and run without errors on 'stu' platform. 

\subsection{Project Specifications}
Project adheres to specifications. socket programming for client/server model and creation of sub-processes for Paper Scissors Rock (PSR) game, conform with project requirements.

\subsection{Development and Debugging Process}
Throughout development process, no significant issues were encountered. 

\section{Code Listings}
\subsection{Play Program}
\lstinputlisting[style=cstyle, caption={play.c}]{play.c}

\subsection{Referee Program}
\lstinputlisting[style=cstyle, caption={referee.c}]{referee.c}

\subsection{Player Program}
\lstinputlisting[style=cstyle, caption={player.c}]{player.c}

\subsection{Readstr Function}
\lstinputlisting[style=cstyle, caption={readstr.c}]{readstr.c}

\subsection{MakeFile}
\lstinputlisting[style=cstyle, caption={Makefile}]{Makefile.mak}

\section*{References}

\begin{enumerate}
  \item Robbins, K. A., \& Robbins, S. (n.d.). \textit{Unix™ Systems Programming: Communication, Concurrency, and Threads}. O'Reilly Media. Retrieved from https://www.oreilly.com
  \item Toptal®. (n.d.). \textit{Beginner's Guide to Concurrent Programming}. Retrieved from https://www.toptal.com
  \item (n.d.). \textit{Start Concurrent: A Gentle Introduction to Concurrent Programming}. Retrieved from https://start-concurrent.github.io
\end{enumerate}

\vfill
\section*{Academic Integrity Pledge}
{\color{red}\textit{“This work complies with JMU honor code. I did not give or receive unauthorized help on this assignment.”}}

\end{document}
